%%\documentclass[a4paper,11pt]{article}
\documentclass[a4paper,11pt]{article}
\usepackage[english]{babel}
\usepackage{epsfig}
\usepackage{wrapfig}
\usepackage{a4wide}
\usepackage{subfigure}
%\usepackage{listings} % Only used in "Code Files Appendix"
\usepackage{amssymb}

\title{Consistent lookup during Churn\\ in Distributed Hash Tables}
\author{Stein Eldar Johnsen}

\begin{document}

\newcommand{\qmark}[1]%
  {{\flqq{}#1\frqq{}}}
\newcommand{\qstring}[1]%
  {{\small\tt"{#1}"}}
\newcommand{\miniquote}[1]%
  {{\flushright\em\small{#1}}}
\renewcommand{\descriptionlabel}[1]%
  {\hspace{\labelsep}\sf{#1}}

\newbox\subfigbox \makeatletter
\newenvironment{subfloat}
{\def\caption##1{\gdef\subcapsave{\relax##1}}%
 \let\subcapsave\@empty \setbox\subfigbox\hbox
 \bgroup} {\egroup \subfigure[\subcapsave]{\box\subfigbox}} \makeatother

%% BEGIN "DOCUMENT"

\maketitle

\section*{Summary}

This thesis was written by Stein Eldar Johnsen beginning 15th August 2003 and delivered by
 1st September 2005 with Svein Erik Bratsberg as mentor. The main topics are consistency and
 distributed hash tables.

One unsolved problem with distributed hash tables is consistent lookup. Various DHTs can
 show \qmark{acceptable} consistency ratings, but no DHT can show \emph{no} lookup inconsistency during
 churn. We chose to use a \emph{structural prevention} strategy to remove inconsistent
 lookup on the basis that \emph{inconsistent lookups are a result of inconsistency in routing
 tables}. We define consistent lookup as a lookup that returns a correct membership state
 from some time \emph{during} lookup.

Churn and especially \qmark{unplanned} membership changes may cause series of inconsistency
 problems if not handled carefully. The combination of a planned membership change
 (e.g. \emph{join}) and an unplanned membership change (e.g. node crash causing a node
 to \emph{leave}) can cause problems needing careful repairing in
 the systems routing tables. Table changes are necessary done in an order that guarantees
 a consistent view over index ownership, and makes the possibility of consistent termination
 at any point during execution.

Other novel solutions include fail-fast disconnected-detection, locking membership
 protocols and pre-join knowledge propagation. All these solutions are shown
 to improve consistency through analysis, and are easily adapted for ring geometry DHTs.

Accord was design to test many of the proposals made in the analysis. We built a
 distributed hash table infrastructure (with no hash table functionality), that used
 membership protocols based on the analysis results. The two main membership protocols were based
 on a 2-level 2-phase commit protocol for \qmark{join}, and simple 2-phase commit with
 distributed operations from a single coordinator for the \qmark{leave} protocol.

The solutions proposed in this thesis are fit for all ring geometry DHTs, and some may
 be adapted for tree geometry DHTs, and some for all DHTs. All of Chord, Bamboo andPastry are
 good DHTs that can be used for testing the proposals, where all or most solutions are
 shown to be possible. Future work includes more testing, simulations and analysis
 of adaptations for different geometries.

\emph{Keywords}; consistency, distributed hash table, membership, membership management,
 membership protocol, failure analysis, membership failure, lookup, consistent lookup.

\pagebreak

\tableofcontents

%\pagebreak

\listoftables

\listoffigures

%\pagebreak

\include{Introduction} % 1

\include{StateOfTheArt} % 2

\include{Problems} % 3

\include{Analysis} % 4

\include{Design} % 5

\include{Conclution} % 6

\appendix
\include{Code}

%\include{Documentation} % <-- eps, ps ... ??  skaff noe HTML -> LATEX (lenge leve Doxygen!) !!!
% - The Classes.
% - Documentation is appended externally (CD-ROM / Digitally)

\pagebreak
\bibliographystyle{unsrt}
\bibliography{oppgave}


\end{document}
